---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Include Tables, Images and Graphs in Leaflet Popups

[![Travis build status](https://travis-ci.org/r-spatial/leafpop.svg?branch=master)](https://travis-ci.org/r-spatial/leafpop)
[![monthly](http://cranlogs.r-pkg.org/badges/leafpop)](https://www.rpackages.io/package/leafpop) 
[![total](http://cranlogs.r-pkg.org/badges/grand-total/leafpop)](https://www.rpackages.io/package/leafpop)
[![CRAN](http://www.r-pkg.org/badges/version/leafpop?color=009999)](https://cran.r-project.org/package=leafpop)
[![status](https://tinyverse.netlify.com/badge/leafpop)](https://CRAN.R-project.org/package=leafpop)

`leafpop` creates HTML strings to embed tables, images or graphs in popups
of interactive maps created with packages 'leaflet' or 'mapview'. Handles
local paths to images on the file system or remote urls. Handles graphs created 
with 'base' graphics, 'lattice' or 'ggplot2' as well as interactive plots created 
with 'htmlwidgets'.

## Installation

You can install the released version of `leafpop` from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
install.packages("leafpop")
```

## Example


### Code of Conduct

Please note that the 'leafpop' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

